---
title: "rsemantica vignette"
author: "Pedro L. Rodríguez"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# About `rsemantica`

This vignette describes the usage of `rsemantica` for fitting models to semantic fluency data.

Keep in mind `rsemantica` is still in development.

### Installation

The dev version of `rsemantica` on GitHub can be installed with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
# devtools::install_github("prodriguezsosa/rsemantica")
```

### Load the package

```{r echo=TRUE}
library(rsemantica)
```

# Example: Fitting a model to semantic fluency data from U.S. based MTurkers

We will use semantic fluency data collected from 1056 MTurk subjects. As cues we selected words that are politically relevant: \texttt{welfare}, \texttt{government}, \texttt{American values}, \texttt{Republican} and \texttt{Democrat}. For each cue, subjects were required to respond with associated words without repetitions. We also collected a series of demographic and political attitudes questions, including party identification and ideology.

```{r echo=TRUE}
data("sft_mturk_us")
```

```{r echo=TRUE}
# compile rstan model (need run only once per session) ----------------------------------------------------
model = stan_model(file = paste(model_dir, model_name = "RW_gauss_wo_rep", ".stan", sep = ""))
```



